\input{base.tex}

% title and contact
\newcommand{\cvtitle}{Backend Developer}

\newcommand{\cvintrosecname}{Summary}

\newcommand{\cvintro}{
    Experienced on web applications development, CI/CD pipelines,
    containerization, infrastructure as code and cloud architectures.
    Familiarity with digital transformation, agile methodologies and DevOps
    culture. Interessed on high performance programming, scalable architectures
    and resilient systems.
}
%----------------------------------------------------------------------------------------


% intro, skills, technologies
\newcommand{\cvskillseca}{Languages}
\newcommand{\cvskillsecb}{DevOps}
\newcommand{\cvskillsecc}{Clouds}
\newcommand{\cvskillsecd}{Databases}
%----------------------------------------------------------------------------------------


% experience
\newcommand{\cvjobexpsecname}{Experience}

% job mz
\newcommand{\cvjobperiodmz}{10/2019 -- present}
\newcommand{\cvjobtitlemz}{Backend Developer}
\newcommand{\cvjobcompanymz}{MZ Group}
\newcommand{\cvjobdescriptionmz}{
    MZ is a consulting with expertise in IR that offers a complete suite of
    solutions for public companies.\newline

    I work dedicated to MZiQ, a productivity suite that features investor
    relationship management, shareholder base management, public data from
    finance institutions and funds, report generation, insights etc. My key
    responsabilities are the development of new features, bug fixes, various
    types of automations, creation of new APIs and services and architecture
    design and implementation of queue-based and microservice-based systems.  I
    also act on data extraction from Postgres and Mongo databases and
    development of pipelines using GitLab-CI. Extensive use of technologies
    such as JS, TS,Python, RabbitMQ, AWS Lambda and Docker.
}

% job a
\newcommand{\cvjobperioda}{05/2019 -- 10/2019}
\newcommand{\cvjobtitlea}{Chatbot Developer}
\newcommand{\cvjobcompanya}{HVAR Consulting}
\newcommand{\cvjobdescriptiona}{
    HVAR offers big data, analytics and AI oriented services and products. It
    is a SAP, Google Cloud and AWS partner in Brazil.\newline

    I participated in the AI team developing chatbots using the technology
    stack from Microsoft (Azure Bot Service, LUIS and CosmoDB), Google
    (Dialogflow and Firebase) and IBM (Watson). I've worked on projects to
    understand the business rules, build dialogues, conversation flows and
    develop microservices and webservices that made use of cognition services
    -- from the providers above -- and third-party APIs in order to automate
    tasks, customer service etc. I've also wrote unit and integration tests for
    dialogs validation, CI/CD pipelines with Azure DevOps and conversation
    telemetry to generate usage metrics and bots hit rate.
}

% job b
\newcommand{\cvjobperiodb}{02/2018 -- 05/2019}
\newcommand{\cvjobtitleb}{Infrastructure Developer}
\newcommand{\cvjobcompanyb}{Rivendel Technology}
\newcommand{\cvjobdescriptionb}{
    Rivendel is a cloud computing, DevOps, data engineering and digital
    transformation specialist.\newline

    At the monitoring team, I've developed tools and automations with Python to
    help monitoring systems and applications, as well a real-time dashboard
    (using JS, jQuery, sockets, Redis and other technologies) for metrics
    aggregation of Zabbix servers and services like PagerDuty and
    Pingdom.\newline

    At the deployment team, I've worked on several projects -- remote and
    on-site -- developing microservices with AWS Lambda (Python, JS, Go and
    Java runtimes), CI/CD pipelines (Travis, Drone-CI, Jenkins etc) and cloud
    infrastructure provisioning as code with Terraform and configuration as
    code with Ansible. I've also developed POCs on technologies like Ruby and
    C\# in order to examplify, on the context of the customer's technology
    stack, the usage of gitflow, pipelines and integrations with AWS and other
    managed services.
}
%----------------------------------------------------------------------------------------


% education
\newcommand{\cveducationsecname}{Education}

% course mba
\newcommand{\cvcourseperiodusp}{10/2021 -- 04/2023}
\newcommand{\cvcoursetitleusp}{Data Science and Analytics MBA}
\newcommand{\cvcourseinstitutionusp}{São Paulo University (USP)}
\newcommand{\cvcoursedescriptionusp}{
    Postgraduate focused on big data, machine learning, data engineering /
    mining / visualization.
}

% course a
\newcommand{\cvcourseperioda}{2015 -- 2018}
\newcommand{\cvcoursetitlea}{Information Systems Bachelor's Degree}
\newcommand{\cvcourseinstitutiona}{Anhembi Morumbi University (AUM)}
\newcommand{\cvcoursedescriptiona}{
    Best graded on: algorithms, programming languages, project management and
    distributed systems.
}
