\input{base.tex}

% title and contact
\newcommand{\cvtitle}{Backend Developer}

\newcommand{\cvintrosecname}{Introduction}

\newcommand{\cvintro}{
    Experienced on web applications development, CI/CD pipelines,
    containerization, infrastructure as a code and cloud architectures.
    Familiarity on digital transformation, agile methodologies and DevOps
    culture. Interessed on high performance development, scalable architectures
    and resilient systems.
}
%----------------------------------------------------------------------------------------


% intro, skills, technologies
\newcommand{\cvskillseca}{Programming}
\newcommand{\cvskillsecb}{DevOps}
\newcommand{\cvskillsecc}{Cloud}
\newcommand{\cvskillsecd}{Databases}
%----------------------------------------------------------------------------------------


% experience
\newcommand{\cvjobexpsecname}{Experience}

% job a
\newcommand{\cvjobperioda}{05/19 -- now}
\newcommand{\cvjobtitlea}{Chatbot Developer}
\newcommand{\cvjobcompanya}{HVAR Consulting}
\newcommand{\cvjobdescriptiona}{
    Chatbots development using the Microsoft Bot Framework techonologies stack
    and Azure services. Usage of the JavaScript SDK on chabots, integrating
    with cognitive services (like LUIS), Application Insights telemetry and
    CI/CD pipelines on Azure DevOps. Unit and integration tests writing to
    dialog, conversation flow and third-party API integration validations.
}

% job b
\newcommand{\cvjobperiodb}{02/18 -- 05/19}
\newcommand{\cvjobtitleb}{Infrastructure Developer}
\newcommand{\cvjobcompanyb}{Rivendel Technology}
\newcommand{\cvjobdescriptionb}{
    At the monitoring team, I've developed utilitaries and automations with
    Python to help the monitoring of systems and applications. I've also
    developed a real-time dashboard (using JavaScript, jQuery, sockets, Redis
    and other technologies) for metric aggregation of Zabbix servers and
    services like PagerDuty and Pingdom.\newline\newline
    At the deployment team, I've worked on several projects -- remote and
    in-loco -- on the development of microservices using AWS Lambda (Python,
    JavaScript and Java runtimes), CI/CD pipelines (Travis, Drone-CI, Jenkins
    etc) and cloud infrastructure provisioning as code with Terraform and
    configuration as code with Ansible. I've also developed POCs (Proof of
    Concepts) on technologies like Ruby and C\# in order to examplify, on the
    context of the customer's technology stack, the gitflow, pipelines and
    integrations with AWS and other managed services usage.
}

% job c
\newcommand{\cvjobperiodc}{11/16 -- 03/17}
\newcommand{\cvjobtitlec}{Solutions Engineer}
\newcommand{\cvjobcompanyc}{Alest Consulting}
\newcommand{\cvjobdescriptionc}{
    Part of the projects team, contributing to the development of JavaScript
    based web applications using Google AppMaker and integrations with the G
    Suite productive tools and Google APIs. Macro development using Google Apps
    Scripts and simple Python webservices.
}
%----------------------------------------------------------------------------------------


% education
\newcommand{\cveducationsecname}{Education}

% course a
\newcommand{\cvcourseperioda}{2015 -- 2018}
\newcommand{\cvcoursetitlea}{Information Systems Bachelor's Degree}
\newcommand{\cvcourseinstitutiona}{Anhembi Morumbi University}
\newcommand{\cvcoursedescriptiona}{
    Best grades on: algorithms, programming languages, programming laboratory,
    projects management, ditributed systems.
}
%----------------------------------------------------------------------------------------


% projects
\newcommand{\cvprojectssecname}{Side Projects}

% project a
\newcommand{\cvprojectnamea}{dora}
\newcommand{\cvprojectbaseurla}{\cvgituser}
\newcommand{\cvprojectdescriptiona}{
    A Python microservice that provides a RESTful API to query domains names
    DNS records.
}

% project b
\newcommand{\cvprojectnameb}{msgboi}
\newcommand{\cvprojectbaseurlb}{\cvgituser}
\newcommand{\cvprojectdescriptionb}{
    A JavaScript microservice that sends notifications on Slack channels from
    GitLab-CI events. Highly customizable and ludicrously small.
}

% project c
\newcommand{\cvprojectnamec}{ansible-stow}
\newcommand{\cvprojectbaseurlc}{\cvgituser}
\newcommand{\cvprojectdescriptionc}{
    An Ansible module that interacts with GNU Stow packages.
}
%----------------------------------------------------------------------------------------


% languages
\newcommand{\cvlanguagessecname}{Languages}

% langs
\newcommand{\cvlanguagea}{\textbf{Portuguese} -- Native}
\newcommand{\cvlanguageb}{\textbf{English} -- Proficient}

